Model LF

### 2022-11-22 max_dp endogen stød.Rmd
Commit

@@

>>>>

## Baseline Scenario 8

```{r}
# Define add-factor list (defining shock)
constantAdjList_bs8 <- list(

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_bs8 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList_bs8
                    )
```

```{r}
###Gengivelse af stød til model
max_dp_bs8 = Shock_bs8$simulation$max_dp
wage_bs8 = Shock_bs8$simulation$wage
komp_r_bs8 = Shock_bs8$simulation$komp_r
part_bs8 = Shock_bs8$simulation$part
yk_ds_bs8 = Shock_bs8$simulation$yk_ds
pc_ds_bs8 = Shock_bs8$simulation$pc_ds
wage_ds_t_bs8 = Shock_bs8$simulation$wage_ds_t
ur_ds_bs8 = Shock_bs8$simulation$ur_ds
emp_bs8 = Shock_bs8$simulation$emp
yd_hk_ds_bs8 = Shock_bs8$simulation$yd_hk_ds
prodk_bs8 = Shock_bs8$simulation$prodk
tilpas_pr_bs8 = Shock_bs8$simulation$tilpas_pr
u_ds_bs8 = Shock_bs8$simulation$u_ds
part_bs8 = Shock_bs8$simulation$part
nben_h_bs8 = Shock_bs8$simulation$nben_h
wage_ds_bs8 = Shock_bs8$simulation$wage_ds
dp_person_bs8 = Shock_bs8$simulation$dp_person
kont_h_ratio_bs8 = Shock_bs8$simulation$kont_h_ratio
lf_bs8 = Shock_bs8$simulation$lf
nl_g_bs8 = Shock_bs8$simulation$nl_g
unemp_bs8 = Shock_bs8$simulation$unemp
yd_hk_ds_bs8 = Shock_bs8$simulation$yd_hk_ds
wage_gap1_bs8 = Shock_bs8$simulation$wage_gap1
wage_gap_bs8 = Shock_bs8$simulation$wage_gap
prod_bs8 = Shock_bs8$simulation$prod
ur_test_bs8 = Shock_bs8$simulation$ur_test
ur_bs8 = Shock_bs8$simulation$ur
y_bs8 = Shock_bs8$simulation$y
yk_bs8 = Shock_bs8$simulation$yk
```

@@

# Scenario 8

```{r}
# Define add-factor list (defining shock)
constantAdjList8 <- list(

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q')

```{r}
# Simulate the model (following shock)
Shock_8 <- SIMULATE(S_model
                    ,simType='DYNAMIC'
                    ,TSRANGE=c(2006,3,2020,1)
                    ,simConvergence=0.00001
                    ,simIterLimit=100
                    ,ConstantAdjustment=constantAdjList8
                    )

yk_ds_08 = Shock_8$simulation$yk_ds
emp_08 = Shock_8$simulation$emp
wage_ds_08= Shock_8$simulation$wage_ds
ur_ds_08 = Shock_8$simulation$ur_ds
pc_ds_08 = Shock_8$simulation$pc_ds
yd_hk_ds_08 = Shock_8$simulation$yd_hk_ds
pconk_ds_08 = Shock_8$simulation$pconk_ds
komp_r_08 = Shock_8$simulation$komp_r
max_dp_08 = Shock_8$simulation$max_dp
nben_h_08 = Shock_8$simulation$nben_h
yd_hk_ds_08 = Shock_8$simulation$yd_hk_ds
ik_08 = Shock_8$simulation$ik
wage_ds_t_08 = Shock_8$simulation$wage_ds_t
nben_h_un_08 = Shock_8$simulation$nben_h_un
nl_g_08 = Shock_8$simulation$nl_g
nsben_h_08 = Shock_8$simulation$nsben_h
dp_person_08 = Shock_8$simulation$dp_person
u_ds_08 = Shock_8$simulation$u_ds
shock_kuld_08 = Shock_8$simulation$shock_kuld
unemp_08 = Shock_8$simulation$unemp
lf_08 = Shock_8$simulation$lf
part_08 = Shock_8$simulation$part
yk_08 = Shock_8$simulation$yk
y_08 = Shock_8$simulation$y
prodk_08 = Shock_8$simulation$prodk
```

```{r}
plot(((unemp_08 - unemp_bs8)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Change in Unemployment", ylim= c(-300, 3000));
lines(((unemp_04 - unemp_bs4)*1000), col= "black");
lines(((unemp_02 - unemp_bs2)*1000), col= "red");
lines(((unemp_01 - unemp_00)*1000), col= "green");
legend("left", legend=c("All channels", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```
